---
title: "Chapter 14. Two-Factor Analysis of Variance"
author: "Likan Zhan"
date: '2017-06-07'
output:
  blogdown::html_page:
    number_sections: true
    toc: true
    fig_width: 12
    fig_height: 8
---


# Figure.14.01

- Define a function to draw interaction plots

```{r, echo = TRUE, eval = TRUE}
ff <- function(
Mean = c(7, 3, 9, 5),
rown = 2,
namer = c("Male", "Female"),
namec = c("Non-Violent", "Violent"),
yylim = c(0, 40)
){
Game <- rep(namec, each = rown)	
coln <- length(Mean) / rown
Sex <- rep(namer, coln)
interaction.plot(
  Game, Sex, Mean,
  ylim = yylim,
  type = "b",
  trace.label = "Sex",
  fixed = TRUE,
  xlab = "Video Game",
  ylab = "Mean of Scores", 
  pch = c(1, 1), 
  lty = c(1, 1), 
  bty = "l",
  font.lab = 2, 
  col = c("#cf232a", "#005093"),
  lwd = 2
  )
}
```

- Do the plotting

```{r label = "Figure_14_01_E1", echo = TRUE, eval = TRUE}
par(mfrow = c(1, 2))
ff(c(20, 10, 20, 10))
ff(c(30, 30, 10, 10))
```

```{r label = "Figure_14_01_E2", echo = TRUE, eval = TRUE}
par(mfrow = c(1, 2))
ff(c(10, 20, 20, 10))
ff(c(10, 20, 30, 40))
```

```{r label = "Figure_14_01_E3", echo = TRUE, eval = TRUE}
par(mfrow = c(1, 2))
ff(c(20, 10, 10, 40))
ff(c(10, 20, 10, 40))
```

# Figure.14.02

- Create the data

```{r, echo = TRUE, eval = TRUE}
data <- c(10, 30, 40, 50, 20, 30)
FactorA <- rep(c("A1", "A2"), 3)
FactorB <- rep(c("B1", "B2", "B3"), each = 2)
sample <- data.frame(
  factorA = FactorA,
  factorB = FactorB,
  score = data
  )
xtabs(score ~ factorA + factorB, data = sample)
```
- Plot the figure

```{r label = "Figure_14_02", echo = TRUE, eval = TRUE}
library(ggplot2)
p1 <- ggplot(data = sample, stat="identity")  + 
aes(x = factorB, y= score, group = factorA, color = factorA) +
geom_line() + geom_point()+
scale_x_discrete(expand = c(0, 0.3)) +
scale_y_continuous(expand = c(0, 0), limits = c(0, 55)) +
scale_color_manual("Factor A", values = c("A1" = "#33609d", "A2" = "#d4493a")) +
xlab("Levels of Factor B") + ylab("Mean of Scores") +
theme(axis.title = element_text(face = "bold"),
  legend.key = element_blank(),
  panel.background = element_blank(),
  axis.line = element_line(colour = "black", size = 0.2)
  )

p2 <- ggplot(data = sample)  + 
aes(x = factorB, y = score, fill = factorA) +
geom_bar(width = 0.4, , stat = "identity", position = position_dodge(width = 0.5)) +
scale_x_discrete(expand=c(0, 0.3)) +
scale_y_continuous(expand = c(0, 0), limits = c(0, 55)) +
scale_fill_manual("Factor A", values = c("A1" = "#33609d", "A2" = "#d4493a")) +
xlab("Levels of Factor B") + ylab("Mean of Scores") +
theme(axis.title = element_text(face = "bold"),
      panel.background=element_blank(),
         axis.line = element_line(colour="black",size=0.2)
      )
gridExtra::grid.arrange(p1, p2, ncol = 2)
```

# Table 14.2 and Figure 14.4

- Create the data set

```{r, echo = TRUE, eval = TRUE}
data <- c(
  11, 8,  9, 10, 7, 
  10, 7, 10,  6, 7, 
   4, 4,  8,  5, 4, 
  10, 6, 10, 10, 9)
TC <- rep(c(rep("Self_regulated", 5), rep("Fixed", 5)), 2) 
PM <- rep(c("Paper", "Computer_screen"), each = 10) 
sample <- data.frame(
  Time_control = TC,
  Presentation_mode = PM,
  score = data
  )
print(sample, row.names = FALSE)
```

- Calculate total variability and toal df

```{r, echo = TRUE, eval = TRUE}
attach(sample)
SST <- sum((score - mean(score))^2)
dft <- length(score) - 1
c(SST, dft)
detach(sample)
```

- Sumarize the data in each cell

```{r, echo = TRUE, eval = TRUE}
library(dplyr, quietly = TRUE)
dtbt <- sample %>% 
  group_by(Time_control, Presentation_mode) %>% 
  summarise(
  n = length(score),   
  M = mean(score), 
  T = sum(score), 
  SS = sum((score - mean(score))^2)
  )  
dtbt <- as.data.frame(dtbt) 
print(dtbt, row.names = FALSE)
```

- Calculate sum of squares between treatments

```{r, echo = TRUE, eval = TRUE}
attach(dtbt, warn.conflicts = FALSE)
SSbt <- sum(5 * (M - mean(M))^2)
dfbt <- length(M) - 1
SSwt <- sum(SS)
dfwt <- sum (n - 1)
detach(dtbt)
c(SSbt, dfbt, SSwt, dfwt)
```

- Sumarize the data based on rows

```{r, echo = TRUE, eval = TRUE}
dtA <- sample %>% 
  group_by(Time_control) %>% 
  summarise(
  n = length(score),   
  M = mean(score), 
  T = sum(score), 
  SS = sum((score - mean(score))^2)
  )  
dtA <- as.data.frame(dtA) 
print(dtA, row.names = FALSE)
```

- Calculate sum of squares of factor A

```{r, echo = TRUE, eval = TRUE}
attach(dtA, warn.conflicts = FALSE)
SSa <- sum(n * (M - mean(M))^2)
dfa <- nrow(dtA) - 1
detach(dtA)
c(SSa, dfa)
```

- Sumarize the data based on columns

```{r, echo = TRUE, eval = TRUE}
dtB <- sample %>% 
  group_by(Presentation_mode) %>% 
  summarise(
  n = length(score),   
  M = mean(score), 
  T = sum(score), 
  SS = sum((score - mean(score))^2)
  )  
dtB <- as.data.frame(dtB)
print(dtB, row.names = FALSE)
```

- Calculate sum of squares of factor B

```{r, echo = TRUE, eval = TRUE}
attach(dtB, warn.conflicts = FALSE)
SSb <- sum(n * (M - mean(M))^2)
dfb <- nrow(dtB) - 1
detach(dtB)
c(SSb, dfb)
```

- Calculate the interaction between A and B

```{r, echo = TRUE, eval = TRUE}
SSab <- SSbt - SSa - SSa
dfab <- dfbt - dfa - dfb
c(SSab, dfab)
```

- Calculate the mean squares

```{r, echo = TRUE, eval = TRUE}
MSwt <- SSwt / dfwt
MSa <- SSa / dfa
MSb <- SSa / dfb
MSab <- SSab / dfab
c(MSwt, MSa, MSab)
```

- Calculate the F-ratio

```{r, echo = TRUE, eval = TRUE}
Fa <- MSa / MSwt
Fb <- MSb / MSwt
Fab <- MSab / MSwt
c(Fa, Fb, Fab)
```

- Calculate levels of significance

```{r, echo = TRUE, eval = TRUE}
pFa <- pf(Fa, dfa, dfwt, lower.tail = FALSE)
pFb <- pf(Fb, dfb, dfwt, lower.tail = FALSE)
pFab <- pf(Fab, dfab, dfwt, lower.tail = FALSE)
c(pFa, pFb, pFab)
```

- Calculate effect size

```{r, echo = TRUE, eval = TRUE}
eta_sqr_a <- SSa / (SSa + SSwt)
eta_sqr_b <- SSb / (SSb + SSwt)
eta_sqr_ab <- SSab / (SSab + SSwt)
c(eta_sqr_a, eta_sqr_b, eta_sqr_ab)
```

- Use `aov()` function

```{r, echo = TRUE, eval = TRUE}
res <- aov(score ~ Time_control * Presentation_mode, data = sample)
summary(res)
```

- Figure 14.4

```{r label = "Figure_14_04", echo = TRUE, eval = TRUE}
dtbt[, "Presentation_mode"] <- factor(
dtbt[, "Presentation_mode"], 
levels <- c("Paper", "Computer_screen"))
with(
  dtbt,
  interaction.plot(
    Presentation_mode, 
    Time_control, 
    M,
    type = "b",
    ylim = c(1, 10),
    trace.label = "Time control",
    fixed = FALSE,
    xlab = "Model of Text Presentation",
    ylab = "Mean of quiz score", 
    pch = c(19, 19), 
    lty = c(1, 1), 
    bty = "l",
    font.lab = 2, 
    col = c("#cf232a", "#005093"),
    lwd = 2
    )
  )
```

# Simple main effects

- Subset the data

```{r}
(ftc <- sample[sample$Time_control == "Self_regulated", ])
```

- Calculate the variance between treatments

```{r}

src <- tapply(ftc$score, ftc$Presentation_mode, mean)
SSsbt <- sum(5 * (src - mean(src))^2)
(MSsbt <- SSsbt / 1)
```

- Calculate the F-value and p value

```{r}
(F_ratio <- MSsbt / MSwt)
pf(F_ratio, 1, 16, lower.tail = FALSE)
```

# Additional variable

- Create the data

```{r}
data <- c(
  3, 8, 4,  0, 6, 1,  2, 4,
  8, 4, 1, 10, 5, 5, 10, 5 
  )
trt <- rep(LETTERS[1:2], each = 8)
sex <- c(
  "M", "F", "F", "M", "F", "M", "F", "M",
  "F", "F", "M", "F", "M", "M", "F", "M"
  )
sample <- data.frame(
  trt = trt,
  score = data,
  sex = sex
  )
print(sample, row.names = FALSE)
```

- Do the analyses

```{r}
summary(aov(score ~ trt, data = sample))
summary(aov(score ~ trt + Error(sex), data = sample)) 
```