---
title: "Probability Distributions in R"
author: "Likan Zhan"
date: '2017-04-01'
output:
  blogdown::html_page:
    toc: true
---

# 1. Introduction

R has a number of built in functions for calculations involving probability distributions, both discrete and continuous, including the `binomial`, `normal`, `Poisson`, `geometric`, `gamma`, `beta`, and others we have seen.

For each distribution, R has four primary functions. Each function has a one letter prefix followed by the root name of the function. The names make mnemonic sense for continuous random variables but are used in both cases. For example `dnorm` is the height of the density of a normal curve while `dbinom` returns the probability of an outcome of a binomial distribution. Here is a table of these commands.

Prefix | Condinuous | Discrete
-|-|-
`d` | density | probability (pmf)
`p` | probability (cdf) | probability (cdf)
`q` | quantile | quantile
`r` | random | random

----

Distribution | root
-|-
Binomial | `binom`
Geometric | `geom`
Hypergeometric|`hyper`
Poisson | `pois`
Normal | `norm`
Gamma | `gamma`
Beta | `beta`
t | `t`
F | `f`
Chi-squre | `chisq`

----

# 2. normal distribution

| Function | Purpose | Example |
| --------|--------|-------- |
| `dnorm(x, mean, sd)` | Probability Density Function (PDF) | `dnorm(0.1, 0, 1)` gives the density (height of the PDF) of the normal 0.1 with mean = 0 and sd = 1 |
| `pnorm(q, mean, sd)` | Cumulative Distribution Function (CDF) | `pnorm(1.96, 0, 1)` gives the area under the standard normal curve to the left of 1.96, i.e., 0.975.|
| `qnorm(q, mean, sd)` | Quantile Function - inverse of pnorm | `qnorm(0.975, 0, 1)` gives the value at which the CDF of the standard normal is 0.975, i.e., 1.96 |
| `rnorm(n, mean, sd)` | Generate random numbers from normal distribution | `rnorm(10, 0, 1)` generate 10 numbers from a normal with mean = 0 and sd =1 |

----


Here are four examples,

```{r eval = TRUE, echo = TRUE}
dnorm(0.1, 0, 1)
pnorm(1.96, 0, 1)
qnorm(0.975, 0, 1)
rnorm(10, 0, 1)
```

# 3. binomial distribution

| Function | Purpose | Example |
| --------|--------|-------- |
| `dbinom(x, size, prob)` | Probability Density Function (PDF) | `dbinom(1, 2, 0.5)` gives the density (height of the PDF) of the binomial 1 with size = 2 and prob = 0.5 |
| `pbinom(q, size, prob)` | Cumulative Distribution Function (CDF) | `pbinom(1, 2, 0.5)` gives the area under the binomial curve to the left of 1, i.e., 0.75.|
| `qbinom(p, size, prob)` | Quantile Function - inverse of pnorm | `qbinom(0.75, 2, 0.5)` gives the value at which the CDF of the binomial is 0.75, i.e., 1.5 |
| `rbinom(n, size, prob)` | Generate random numbers from normal distribution | `rbinom(20, 2, 0.5)` generate 4 numbers from a binomial with size = 2 and probability = 0.5 |

----


Here are four examples,

```{r eval = TRUE, echo = TRUE}
dbinom(1, 2, 0.5)
pbinom(1, 2, 0.5)
qbinom(0.75, 2, 0.5)
rbinom(20, 2, 0.5)
```
