\documentclass[10pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
\usepackage[unicode=true]{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
\hypersetup{
            pdftitle={Curriculum Vitae},
            colorlinks=true,
            linkcolor=Maroon,
            citecolor=Blue,
            urlcolor=blue,
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage[margin=1in]{geometry}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\usepackage[fontsize=13pt]{scrextend}
\usepackage{ctex}
\usepackage{fontspec}
\setmainfont{Optima} % English font
\setCJKmainfont{STKaiti} % Chinese serif font: Source Han Serif SC
\usepackage{hyperref}
%% 2. Change page style
\usepackage{datetime2}
\usepackage{fancyhdr}
\usepackage{lastpage} % LastPage
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\lhead{}
\rhead{Likan Zhan's CV}
\rfoot{Last update: \today}
\fancyfoot[C]{--~\thepage/\pageref*{LastPage}~--}

\title{Curriculum Vitae}
\date{2016-01-22}

\begin{document}
%\maketitle

\hypertarget{likan-zhan}{%
\section{Likan Zhan}\label{likan-zhan}}

\begin{itemize}
\tightlist
\item
  Add: 15, Xueyuan Rd., Haidian District, Beijing 100083, China
\item
  Tel: +86 10 8230 3468
\item
  Email: zhanlikan AT hotmail.com
\item
  Personal website: \url{https://likan.info}
\end{itemize}

\hypertarget{academic-appointment}{%
\subsection{Academic appointment}\label{academic-appointment}}

\begin{itemize}
\tightlist
\item
  2014.10 \textasciitilde{} Now, Assistant professor,\\
  MEG Laboratory for Brain Sciences, \\
  Institute for Speech Pathology and the Brain Science,\\
  Beijing Language and Culture University, Beijing, China
\end{itemize}

\hypertarget{education}{%
\subsection{Education}\label{education}}

\begin{itemize}
\item
  2010.10 \textasciitilde{} 2014.09, Ph.D.~Cognitive Science, \\
  Macquarie University, Sydney, Australia
\item
  2007.09 \textasciitilde{} 2010.07, M.E. Cognitive Psychology, \\
  Beijing Language and Culture University, Beijing, China
\item
  2000.09 \textasciitilde{} 2004.07, B.A. Teaching Chinese as a Second
  Language, \\
  Beijing Language and Culture University, Beijing, China
\end{itemize}

\hypertarget{teaching-responsibilities}{%
\subsection{Teaching responsibilities}\label{teaching-responsibilities}}

\begin{itemize}
\item
  Statistics for the Behavioral Sciences,
  \href{https://likan.info/en/teach/Statistics-for-the-Behavioral-Sciences/}{More
  Info \ldots{}}
\item
  R for Modeling and Visualizing Data,
  \href{https://likan.info/en/teach/R-for-Statistics-Data-Visualization/}{More
  Info \ldots{}}
\item
  Introduction to Cognitive Neuroscience,
  \href{https://likan.info/en/teach/Introduction-to-Cognitive-Neuroscience/}{More
  Info \ldots{}}
\item
  Foundations of Scientific Research,
  \href{https://likan.info/en/teach/Science-and-Scientific-Research/}{More
  Info \ldots{}}
\end{itemize}

\hypertarget{professional-skills}{%
\subsection{Professional skills}\label{professional-skills}}

\begin{itemize}
\item
  Statistics. I teached two statistical courses to master students. I
  have moderate experience in using \emph{R} for statistical modeling
  and data visualization. Besides the basic ones, I used the following R
  packages a lot: \href{http://r-datatable.com}{\emph{data.table}},
  \href{http://dplyr.tidyverse.org}{\emph{dplyr}},
  \href{http://ggplot2.tidyverse.org}{\emph{ggplot2}},
  \href{https://cran.r-project.org/web/packages/car/index.html}{\emph{car}},
  \href{https://github.com/lme4/lme4}{\emph{lme4}},
  \href{https://cran.r-project.org/web/packages/gam/index.html}{\emph{gam}}
  etc. I also created a R package myself, called
  \href{https://github.com/likanzhan/acqr}{\emph{acqr}}.
\item
  Experimental techniques. I'm familiar with
  \href{https://www.pstnet.com/eprime.cfm}{E-prime},
  \href{http://www.psychopy.org}{Psychopy},
  \href{http://psychtoolbox.org}{Psychtoolbox}, and
  \href{https://www.neurobs.com/presentation}{Presentation} for
  presenting test stimuli. I have advanced experience in using Eyelink
  II/1000 plus (SR Research Ltd.), such as \emph{Experiment Builder} for
  experiment building, and \emph{Data Viewer} for data analysis. I am in
  charge of establishing the first Child MEG lab in China, familiar with
  \emph{Yokogawa} MEG system for equipment maintenance and MEG data
  acquisition. I'm also familiar with \emph{BESA}, and some Matlab
  packages for analyzing the E/MEG data, such as
  \href{http://www.fieldtriptoolbox.org}{\emph{fieldtrip}} and
  \href{https://github.com/neurodebian/spm12}{\emph{SPM12}}.
\item
  Typesetting. I like to write with LaTeX, Markdown, and R Markdown. I
  created a \href{https://likan.info}{personal website} with
  \href{https://gohugo.io}{\emph{hugo}} and
  \href{https://github.com/rstudio/blogdown}{\emph{blogdown}}.
\end{itemize}

\hypertarget{grants-and-awards}{%
\subsection{Grants and awards}\label{grants-and-awards}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Grants
\end{enumerate}

\begin{itemize}
\item
  2015 - 2016. Experimental explorations of possible world semantics,
  The Fundamental Re- search Funds for the Central Universities,
  {[}Grant No.: 15YBB29{]}, Zhan, L., ¥20,000.
\item
  2015 - 2016. Introduction to psychology and introduction to scienti c
  research, The Funds Supporting the Growth of the New Teachers,
  {[}Grant No.: FD201530{]}, Zhan, L., ¥7,000.
\item
  2015 - 2016. Processing and acquisition of tone perception in Mandarin
  Chinese, The Fundamental Research Funds for the Central Universities,
  {[}Grant No.: 15YJ050003{]}, Zhan, L., Shi, F., Gao, L., \& Zhang, L.,
  ¥70,000.
\item
  2010 - 2014. The interpretation of conditionals in natural language,
  Cognitive Science Post- graduate Research Grant of Macquarie
  University, Zhan, L., \$10,570.
\item
  2013.10. The hypothetical property of conditionals in natural
  language, Macquarie University Postgraduate Research Fund, Zhan, L.,
  \$4,684.
\end{itemize}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{1}
\tightlist
\item
  Awards
\end{enumerate}

\begin{itemize}
\item
  2013.11. 38th Boston University Conference on Language Development,
  Paula Menyuk Travel Award, \$300.
\item
  2013.04. 26th Annual CUNY Sentence Processing Conference, Travel
  Award, \$350.
\end{itemize}

\hypertarget{publications}{%
\subsection{Publications}\label{publications}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Book
\end{enumerate}

\begin{itemize}
\tightlist
\item
  \textbf{Zhan, L.} (2015). \emph{The Interpretation of Conditionals in
  Natural Language}. Saarbrucken, Germany: Lap Lambert Academic
  Publishing.
\end{itemize}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{1}
\tightlist
\item
  Periodicals
\end{enumerate}

\begin{itemize}
\item
  \textbf{Zhan, L.} (2018). Using eye movements recorded in the visual
  world paradigm to explore the online processing of spoken language.
  \emph{Journal of Visualized Experiments, 140}, e58086. doi:
  10.3791/58086
  \href{https://publications.likan.info/jove-protocol-58086.pdf}{FullText}
\item
  Zhou, P., Ma, W., \textbf{Zhan, L.}, \& Ma, H (2018). Using the visual
  world paradigm to study sentence comprehension in Mandarin-speaking
  children with autism. \emph{Journal of Visualized Experiments, 140},
  e58452. doi: 10.3791/58452
  \href{https://publications.likan.info/jove-protocol-58452.pdf}{FullText}
\item
  \textbf{Zhan, L.}, Zhou, P., \& Crain, S. (2018). Using the
  visual-world paradigm to explore the meaning of conditionals in
  natural language. \emph{Language, Cognition and Neuroscience, 33}(8),
  1049-1062. doi: 10.1080/23273798.2018.1448935
  \href{https://publications.likan.info/LangCognNeurosci2018.pdf}{FullText}
\item
  \textbf{Zhan, L.} (2018). Scalar and ignorance inferences are both
  computed immediately upon encountering the sentential connective: The
  online processing of sentences with disjunction using the visual world
  paradigm. \emph{Frontiers in Psychology, 9}. doi:
  10.3389/fpsyg.2018.00061
  \href{https://www.frontiersin.org/articles/10.3389/fpsyg.2018.00061/full}{FullText}
\item
  Moscati, V., \textbf{Zhan, L.}, \& Zhou, P. (2017). Children's on-line
  processing of epistemic modals. \emph{Journal of Child Language,
  44}(5), 1025-1040. doi: 10.1017/S0305000916000313\\
   \href{https://publications.likan.info/JChildLang2016.pdf}{FullText}
\item
  \textbf{Zhan, L.}, Crain, S., \& Zhou, P. (2015). The online
  processing of only if- and even if- conditional statements:
  Implications for mental models. \emph{Journal of Cognitive Psychology,
  26}(7), 367-379. doi: 10.1080/ 20445911.2015.1016527
  \href{https://publications.likan.info/JCognPsychol2015.pdf}{FullText}
\item
  Zhou, P., Crain, S., \& \textbf{Zhan, L.} (2014). Grammatical aspect
  and event recognition in children's online sentence comprehension.
  \emph{Cognition, 133}(1), 262-276. doi:
  10.1016/j.cognition.2014.06.018
  \href{http://publications.likan.info/Cognition2014.pdf}{FullText}
\item
  Zhou, P., Crain, S., \& \textbf{Zhan, L.} (2012). Sometimes children
  are as good as adults: The pragmatic use of prosody in children's
  on-line sentence processing. \emph{Journal of Memory and Language,
  67}(1), 149-164. doi: 10.1016/j.jml.2012.03.005
  \href{https://publications.likan.info/JMemLang2012.pdf}{FullText}
\item
  Zhou, P., Su, Y., Crain, S., Gao, L., \& \textbf{Zhan, L.} (2012).
  Children's use of phonological information in ambiguity resolution: a
  view from Mandarin Chinese. \emph{Journal of Child Language, 39}(04),
  687-730. doi: 10.1017/S0305000911000249
  \href{https://publications.likan.info/JChildLang2012.pdf}{FullText}
\end{itemize}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{2}
\tightlist
\item
  Conference proceedings
\end{enumerate}

\begin{itemize}
\tightlist
\item
  \textbf{Zhan, L.}, Crain, S., \& Zhou, P. (2013). The anticipatory e
  ects of focus operators: A visual- world paradigm eye-tracking study
  of ``only if'' and ``even if'' conditionals. In N. Goto, K. Otaki, A.
  Sato, \& K. Takita (Eds.), \emph{Proceedings of GLOW in Asia IX 2012}.
  Mie University, Japan.
\end{itemize}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{3}
\tightlist
\item
  Conference presentations
\end{enumerate}

\begin{itemize}
\item
  \textbf{Zhan, L.} (2017, September). \emph{Scalar implicature and
  ignorance inference are both locally computed: Evidence from the
  online processing of disjunctions using the visual world paradigm}.
  Paper presented at the Second High-level Forum on Cognitive
  Linguistics, University of International Business and Economics,
  Beijing, China
\item
  Moscati, V., \textbf{Zhan, L.}, \& Zhou, P. (2013). Reasoning on
  possibilities: An eye tracking study on modal knowledge. In \emph{the
  38th Annual Boston University Conference on Language Development}.
  Boston, USA.
\item
  \textbf{Zhan, L.}, Crain, S., \& Zhou, P. (2013). Going beyond the
  information that is perceived: The hypothetical property of
  if-conditionals in Mandarin Chinese. In the \emph{Second International
  Conference on Psycholinguistics in China}. Fuzhou, China.
\item
  \textbf{Zhan, L.}, Crain, S., \& Zhou, P. (2013). The hypothetical
  property of ``if''-statements: A visual- world paradigm eye-tracking
  study. In \emph{CUNY2013: The 26th annual CUNY Sentence Processing
  Conference}. Columbia, SC.
\item
  \textbf{Zhan, L.}, Crain, S., \& Zhou, P. (2013). The interpretation
  of conditionals. In \emph{the 7th International Conference on Thinking
  (ICT2012)}. Birkbeck/UCL, London, UK.
\item
  Zhou, P., Crain, S., \& \textbf{Zhan, L.} (2013). Anticipatory eye
  movements in children's processing of grammatical aspect. In \emph{the
  38th Annual Boston University Conference on Language Development}.
  Boston University, United States.
\item
  Zhou, P., Crain, S., \& \textbf{Zhan, L.} (2012). Children's pragmatic
  use of prosody in sentence processing. In \emph{the 35th Generative
  Linguistics in the Old World (GLOW) Workshop: Production and
  Perception of Prosodically-Encoded Information Structure}. University
  of Potsdam, Potsdam, Germany.
\item
  \textbf{Zhan, L.}, Crain, S., \& Khlentzos, D. (2011). The basic
  semantics of conditionals in natural language. In \emph{The
  Harvard-Australia Workshop on: Language, Learning and Logic}.
  Macquarie University, Sydney, Australia.
\item
  Zhou, P., Crain, S., Gao, L., \& \textbf{Zhan, L.} (2010). The role of
  prosody in children's focus identi cation. In \emph{the Generative
  Approaches to Language Acquisition - North America 4 (GALANA- 4)}.
  Toronto, Canada.
\item
  Zhou, P., Su, Y., Crain, S., Gao, L., \& \textbf{Zhan, L.} (2010).
  Children's use of prosodic information in ambiguity resolution. In
  \emph{the 8th Conference of Generative Linguistics in the Old World
  Asia (GLOW-in-Asia 8)}. Beijing, China.
\end{itemize}

\end{document}
